%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tfrupee}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
 \vspace{-1pt}
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.05in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Gaurav Galiyawala} \\ \vspace{1pt}
    \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{galiyawalagaurav@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/gaurav-galiyawala-89b079214}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/GK-07}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {C.B. Patel Computer College}{Surat, Gujarat}
      {Bachelor of Computer Application  \textbf{8.85 CGPA}}{June 2018 -- June 2021}
    \resumeSubheading
       {MIT World Peace University}{Pune, Maharashtra}
      {Master of Computer Application  \textbf{9.54 CGPA}}{August 2021 -- May 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Product Engineer (Full Stack)}{January 2023 -- June 2023}
      {vInnovate Technologies LLC}{Lonavala, Maharashtra}
      \resumeItemListStart
        \resumeItem{Collaborated with a cross-functional team to define and refine project requirements, ensuring clear objectives.}
        \resumeItem{Developed backend logic and APIs using Laravel. Created responsive user interfaces and frontend components using React, HTML, and CSS. Implemented database models and migrations with Laravel's Eloquent ORM.}
        \resumeItem{ Utilized Git for version control and participated in code reviews with team members.}
         \resumeItem{Wrote and maintained server-side code and API endpoints using Node.js and Express.js.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Doccure} $|$ \emph{Bootstrap, CodeIgniter, CKEditor, MySQL, InstaMojo, Vonage(Vide Call)}}{April 2021}
          \resumeItemListStart
            \resumeItem{Facilitates virtual consultations, connecting patients with healthcare professionals.}
            \resumeItem{Streamlines the diagnostic process by enabling prescription uploads and report generation through integrated laboratories.Improves healthcare accessibility and convenience for users.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Hospital Management System} $|$ \emph{ASP.NET, C\#, MS SQL Server}}{March 2022}
          \resumeItemListStart
            \resumeItem{Developed a Hospital Management System to streamline patient care, appointment handling, billing, and resource management.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{BioMedic} $|$ \emph{Flutter, Firebase, Android, Stripe}}{November 2022}
          \resumeItemListStart
            \resumeItem{Established an online platform for the purchase of medical products, medications, and healthcare supplies.}
            \resumeItem{Integrated a secure payment gateway to facilitate hassle-free online transactions.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Facepedia} $|$ \emph{React, Express.js, Node.js, Mongoose, MongoDB}}{July 2023}
          \resumeItemListStart
            \resumeItem{Engineered a dynamic social media platform using the MERN stack, incorporating essential libraries such as Multer for file handling, Morgan for logging, Helmet for security, and Bcrypt for password encryption.}
            \resumeItem{Implemented robust user authentication and authorization mechanisms to ensure data security and privacy.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{3D Tshirt Design} $|$ \emph{React, Express.js, Node.js, three.js}}{August 2023}
          \resumeItemListStart
            \resumeItem{Developed an interactive 3D T-shirt design platform using React, Node, Express, and Three.js.}
            \resumeItem{Integrated OpenAI's DALL·E API, allowing users to generate unique T-shirt designs based on prompts, expanding creative options.}
            \resumeItem{Provided an engaging and user-friendly experience for designing and visualizing custom T-shirts, leveraging advanced 3D modeling features.}
        
          \resumeItemListEnd
         \resumeProjectHeading
          {\textbf{Thread Clone} $|$ \emph{Next.js, Clerk, Tailwind }}{September 2023}
          \resumeItemListStart
            \resumeItem{Professionally architected and executed a Next.js-powered thread cloning application, adeptly incorporating Clerk login for advanced user security and access control. }
            \resumeItem{Demonstrated hands-on experience in utilizing Tailwind CSS for responsive and visually engaging user interfaces, aligning with best practices in web development.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Overall Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (MySQL, PL/SQL, MS SQL), JavaScript, HTML/CSS, C\#} \\
     \textbf{Frameworks}{: React, Node.js, CodeIgniter, Laravel, Next.js, Express.js, Bootstrap} \\
     \textbf{Developer Tools}{: Git, Docker,  VS Code, Visual Studio, Android Studio, AWS} \\
     \textbf{Hobbies \& Soft Skills}{: Coding, Singing, Travelling, Leadership, Management, Communication}\\
    }}
\end{itemize}
\section{Achievements \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Achievements}{: Scholarship \textbf{85,000\rupee  (MIT-WPU)}, IT Quiz Competition \textbf{(Symbiosis, S.D. Jain College)}, C++ Codezz Winner}\\
     \textbf{Certifications \& Training}{: Core Java, React, Git, Unix, Docker, SQLServer by \textbf{IIHT}}\\
    }}

\end{itemize}
 


%-------------------------------------------
\end{document}
